### 2011-08-20 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

MDL is the most important step. It ranks each DTD candidate using two aspects - conciseness and preciseness. Conciseness of a DTD is expressed using the number of bits required to describe the DTD (the smaller, the better). Preciseness of a DTD is expressed using the number of bits required for description of the input data using the DTD. In other words, the more accurately the structure is described, the fewer bits are required. Since the two conditions are contradictory, their balancing brings reasonable and realistic results.

\subsection{SchemaMiner}
The SchemaMiner system \todo{bibref} is an example of \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focusses on inferring elements with the same name but different structure and unordered sequences.

@@

\section{Discovering XML Keys and Foreign Keys in Queries}
This methods tries to improve automatic XML schema inference by discovering keys and foreign keys from a set of XQuery queries. Just these queries are utilized in inference, no XML data are used. The output of this method is a set of keys and foreign keys that can be captured using XML Schema \textbf{key}, \textbf{keyref} \todo{aj unique?} constructs.

@@

\begin{define}[Key]
A key is a construct $$(C, P, \{L\})$$ where $C$, $P$, $L$ are XPath paths without predicates thet use only \texttt{child} and \texttt{descendant} axes.
$C$ can be omitted. $(P, \{L\})$ is then equivalent to $(/, P, \{L\})$ and is called \emph{global key}.Otherwise it is called \emph{local key}.
\end{define}

@@

\begin{define}[Foreign key]
A foreign key is a construct $$(C, (P_1, \{L_1\}) \Rightarrow (P_2, \{L_2\}))$$ where $(C, P_2, \{L_2\})$ is a key, $P_1$, $L_1$ are XPath paths without predicates thet use only \texttt{child} and \texttt{descendant} axes.
$C$ can be omitted as in the case of keys.
\end{define}

@@

\subsection{Key and foreign key discovery}
\subsubsection{Joins in queries}
To discover keys and foreign keys, method utilizes element/element joins.

@@

\subsubsection{Join patterns}
For a certain join, the decision for one of the cases (O1) and (O2) is made by the form of the join. The query is searched for so-called \emph{join patters}. These are \texttt{for} \emph{join pattern} and \texttt{let} \emph{join pattern} and look like the following (the first is \texttt{for} \emph{join pattern}, the second is \texttt{let} \emph{join pattern}):
\todo[inline]{spravne kreslit indexy pri pismenkach}
\begin{verbatim}
01  for e1 in P1               for $e1 in P1
02  return                     return
03    for $e2 in                 let $e2 :=
        P2[L2 = $e1/L1]            P2[L2 = $e1/L1]
04    return CR                  return CR
\end{verbatim}

@@

\section{Conclusion}
The output of our method is a list of scored keys and for each key a list foreign keys referencing the key. The score of a key can be negative or positive. A negative score means that the key is not specified by the XML documents while positive means that it is satisfied. The absolute value of the score means how sure the method is about it.

>>>>

MDL is the most important step. It ranks each DTD candidate using two aspects - conciseness and preciseness. Conciseness of a DTD is expressed by using the number of bits required to describe the DTD (the smaller, the better). Preciseness of a DTD is expressed using the number of bits required for description of the input data using the DTD. In other words, the more accurately the structure is described, the fewer bits are required. Since the two conditions are contradictory, their balancing brings reasonable and realistic results.

\subsection{SchemaMiner}
The SchemaMiner system \todo{bibref} is an example of \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.

@@

\section{Discovering XML Keys and Foreign Keys in Queries}
This method tries to improve automatic XML schema inference by discovering keys and foreign keys from a set of XQuery queries. Just these queries are utilized in inference, no XML data are used. The output of this method is a set of keys and foreign keys that can be captured using XML Schema \textbf{key}, \textbf{keyref} \todo{aj unique?} constructs.

@@

\begin{define}[Key]
A key is a construct $$(C, P, \{L\})$$ where $C$, $P$, $L$ are XPath paths without predicates that use only \texttt{child} and \texttt{descendant} axes.
$C$ can be omitted. $(P, \{L\})$ is then equivalent to $(/, P, \{L\})$ and is called \emph{global key}. Otherwise it is called \emph{local key}.
\end{define}

@@

\begin{define}[Foreign key]
A foreign key is a construct $$(C, (P_1, \{L_1\}) \Rightarrow (P_2, \{L_2\}))$$ where $(C, P_2, \{L_2\})$ is a key, $P_1$, $L_1$ are XPath paths without predicates that use only \texttt{child} and \texttt{descendant} axes.
$C$ can be omitted as in the case of keys.
\end{define}

@@

\subsection{Key and foreign key discovery}
\subsubsection{Joins in queries}
To discover keys and foreign keys, the described method utilizes element/element joins.

@@

\subsubsection{Join patterns}
For a certain join, the decision for one of the cases (O1) and (O2) is made by the form of the join. The query is searched for so-called \emph{join patters}. These are \texttt{for} \emph{join pattern} and \texttt{let} \emph{join pattern} and look as following (the first is \texttt{for} \emph{join pattern}, the second is \texttt{let} \emph{join pattern}):
\todo[inline]{spravne kreslit indexy pri pismenkach}
\begin{verbatim}
01  for e1 in P1               for $e1 in P1
02  return                     return
03    for $e2 in                 let $e2 :=
        P2[L2 = $e1/L1]            P2[L2 = $e1/L1]
04    return CR                  return CR
\end{verbatim}

@@

\section{Conclusion}
The output of the method is a list of scored keys and for each key a list foreign keys referencing the key. The score of a key can be negative or positive. A negative score means that the key is not specified by the XML documents while positive means that it is satisfied. The absolute value of the score means how sure the method is about it.
